maxent model avec xvalidation (year-based test training)

### 2019-05-16 src/maxent_avec_xvalidation.Rmd
cells used in all months

start with mpa binary map first

```{r}

@@

>>>>

start with mpa binary map first - based on averages

```{r get all csvs in one database}
mthlst <- c("jan", "mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
stdep <- read.csv("../output/maxent/models/dec1998/stack_depth.csv", header = TRUE)
depthlayers <- data.frame(cbind(unique(stdep$ascdepths)))
names(depthlayers)[names(depthlayers) == "cbind.unique.stdep.ascdepths.."] <- "depth"
depthlayers$depth <- as.character(depthlayers$depth)

for(m in 1:length(mthlst)){
  mthna <- mthlst[m]
#mthna <- "jan"
  mpabin_lst <- list.files(paste0("../output/maxent/predictions/", mthna), pattern =  "^binary_avg_cloglog.*.asc", full.names = TRUE)

  for (d in 1:nrow(depthlayers)){
    dep <- depthlayers$depth[d]
    for (a in 1:length(mpabin_lst)){
      asc <- mpabin_lst[a]
      if (grepl(dep, asc)){
        depthlayers[d , paste0(mthna)] <- asc

      }
    }
  }
  write.csv(depthlayers, ("../output/maxent/predictions/all_cells/binary_avg_asclayerbydepth.csv"), row.names = FALSE)
}

@@

```{r create stacks by depth}
depthlayers <- read.csv("../output/maxent/predictions/all_cells/binary_avg_asclayerbydepth.csv", header = TRUE)

for (x in 1:nrow(depthlayers)){
  asclay <- depthlayers[x, ]
  asclay <- asclay[!is.na(asclay)]
  asclay <- as.data.frame(rbind(asclay))
  asclay$V1 <- as.character(asclay$V1) #v1 corresponds to depth
  asclay$V2 <- as.character(asclay$V2) #v2 to end corresponds to month
  asclay$V3 <- as.character(asclay$V3)
  asclay$V4 <- as.character(asclay$V4)
  asclay$V5 <- as.character(asclay$V5)
  asclay$V6 <- as.character(asclay$V6)
  asclay$V7 <- as.character(asclay$V7)
  asclay$V8 <- as.character(asclay$V8)
  asclay$V9 <- as.character(asclay$V9)
  asclay$V10 <- as.character(asclay$V10)
  asclay$V11 <- as.character(asclay$V11)
  asclay$V12 <- as.character(asclay$V12)

  ascjan <- raster(asclay$V2)
  ascmar <- raster(asclay$V3)
  ascapr <- raster(asclay$V4)
  ascmay <- raster(asclay$V5)
  ascjun <- raster(asclay$V6)
  ascjul <- raster(asclay$V7)
  ascaug <- raster(asclay$V8)
  ascsep <- raster(asclay$V9)
  ascoct <- raster(asclay$V10)
  ascnov <- raster(asclay$V11)
  ascdec <- raster(asclay$V12)

  stkasc <- stack(ascjan, ascmar, ascapr, ascmay, ascjun, ascjul, ascaug, ascsep, ascoct, ascnov, ascdec)

  avg <- sum(stkasc, na.rm = TRUE)

  writeRaster(avg, paste0("../output/maxent/predictions/all_cells/count_cells_used_all_months_mpa", asclaydep, ".asc"), overwrite=TRUE)
  avgplot <- plot(avg, png(paste0("../output/maxent/predictions/all_cells/count_cells_used_all_months_mpa", asclaydep, ".png")), overwrite = TRUE) 
  dev.off()
}

```{r create rasters showing cells that are suitable in all 11 months}
cellslst <- list.files("../output/maxent/predictions/all_cells", pattern =  "^count_cells_used_all_months_mpa.*.asc", full.names = TRUE)

allcell <- function(x){
  ifelse(x == 12, 1,
  ifelse(x < 12, 0, NA)) 
}

for (r in 1:length(cellslst)){
  ras <- raster(cellslst[r])
  ascname <- names(ras)
  allc <- calc(ras, fun = allcell)
  writeRaster(allc, paste0("../output/maxent/predictions/all_cells/total_cells_used_all_months_mpa", ascname, ".asc"), overwrite = TRUE)
  plot(allc, png(paste0("../output/maxent/predictions/all_cells/total_cells_used_all_months_mpa", ascname, ".png")), overwrite = TRUE)
  dev.off() # stops automatic saving of the plot to a png

}
```

there are no cells that are used in every month....
